\text{Additive drift with tail bounds}

### 2021-09-25 article.tex
add graphics

% \documentclass[8pt, a4paper, twocolumn]{article}
\documentclass[12pt, a4paper]{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{indentfirst}
\usepackage{graphicx}
\usepackage{mathtext}
\usepackage[T1,T2A]{fontenc}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{stmaryrd}
\usepackage{a4wide}

\lstset{basicstyle=\ttfamily\footnotesize,breaklines=true}

\title{\text{Additive drift with tail bounds}}

@@

    If there are constants $\lambda > 0$ and $D \ge 1$ and a $p$ taking only positive values, for which the following four conditions hold
    \renewcommand\labelenumi{(\theenumi)}
    \begin{enumerate}
        \item $\gfun(X_0) \ge b$,
        \item $\forall t \ge 0 : E\left[e^{-\lambda(\gfun(X_{t + 1} - \gfun(X_t)))} |\ X_t,\ \gfun(X_t) < b\right] \leq 1 - \frac{1}{p} = \rho$,
        \item $\forall t \ge 0 : E\left[e^{-\lambda(\gfun(X_{t + 1} - b))} |\ X_t,\ \gfun(X_t) \ge b\right] \leq D$,
    \end{enumerate}
    then for all time bounds $B \ge 0$ the probability that $T$ exceeds $B$ is at most:

@@

\begin{lemma}[Lemma 2.8 in \cite{Hajek 82}] \label{lm:haj}
    If conditions 2 and 3 are met then for all $t \geq 0$:

@@

    \begin{align*}
        \Pr[T \leq B] &= \sum_{k=1}^{B} \Pr[T = k] \\
        &= \sum_{k=1}^{B} \Pr[\gfun(X_k) \leq a \land \gfun(X_{k - 1}) > a \land ... \land \gfun(X_0) > a)] \\
        & \leq \sum_{k=1}^{B} \Pr[\gfun(X_k) \leq a].
    \end{align*}

@@

    \begin{align*}
        \Pr[T \leq B] & \leq \sum_{k=1}^{B} \left(\rho^k e^{\lambda(a - \gfun(X_0))} + \frac{1 - \rho^k}{1 - \rho} D e^{\lambda(a - b)}\right)\\
        & = \rho \left(\frac{1 - \rho^B}{1 - \rho}\right) e^{\lambda a}\left(e^{-\lambda\gfun(X_0)} - \frac{D}{1 - \rho} e^{-\lambda b}\right) + e^{\lambda(a - b)} \frac{B D}{1 - \rho}.
    \end{align*}

@@

\end{proof}
\subsection{Theorem for sub-gaussian processes}
\cm
\subsection{Comparing requirements}
To use some versions of drift theorems, we need some requirements on the sequence of random variables to be satisfied, such as the following:
$$
\exists \delta \geq 0,\ c \in \mathbb{R} \ \forall  t \geq 0 \ \forall \gamma \in [0, \delta]: $$$$
E\left[e^{\gamma (X_{t + 1} - X_{t})}\right] \leq e^{\frac{c \gamma^2}{2}},$$

@@

$$\exists \delta \geq 0,\ p \geq 1 \ \forall t \geq 0: $$$$
E\left[e^{\gamma (X_{t + 1} - X_{t})}\right] \leq 1 - \frac{1}{p}\ .$$

@@

Consider the definition of expectation of a function:
\[
E[e^{\gamma X}] = \int_{-\infty}^{+\infty} f(x) e^{\gamma x} \,dx,    
\]

where $f(x)$ is a distribution density function.

@@

Let's take the first derivative $\gamma$:

\begin{align*}
\frac{\partial E[e^{\gamma X}]}{\partial \gamma} &= \frac{\partial}{\partial \gamma} \int_{-\infty}^{+\infty} f(x) e^{\gamma x} \, dx = \int_{-\infty}^{+\infty} f(x) \frac{\partial e^{\gamma x}}{\partial \gamma} \, dx = \int_{-\infty}^{+\infty} x f(x) e^{\gamma x} \, dx = \\
&= \int_{-\infty}^{0} x f(x) e^{\gamma x} \, dx + \int_{0}^{+\infty} x f(x) e^{\gamma x} \, dx.
\end{align*}

Note that $\forall x \leq 0 : e^{\gamma x} \leq 1$ and $\forall x \geq 0 : e^{\gamma x} \geq 1 + \gamma x$. Hence because $\forall x : f(x) \geq 0$

\begin{align*}
    \int_{0}^{+\infty} x f(x) e^{\gamma x} \, dx &\geq \int_{0}^{+\infty} x f(x) (1 + \gamma x)\, dx    \\
    \int_{-\infty}^{0} x f(x) e^{\gamma x} \, dx &\geq \int_{-\infty}^{0} x f(x)\, dx.    
\end{align*}

@@

\begin{align*}
\frac{\partial E[e^{\gamma X}]}{\partial \gamma} &\geq  \int_{0}^{+\infty} x f(x) (1 + \gamma x)\, dx + \int_{-\infty}^{0} x f(x)\, dx  \\
&= E[X] + \gamma \int_{0}^{+\infty} x^2 f(x) \, dx.
\end{align*}

Denote $\int_{0}^{+\infty} x^2 f(x) \, dx = c \geq 0$ and then if we reintegrate back, we get a restriction on the expectation from below:

@@

In the same way consider expectation of function by definition:

@@

After taking the first derivative we may split terms from $P$ set with other: 
% В таком случае, аналогично возьмем производную и рассмотрим пот отдельности слагаемые из множества P и остальные:

\begin{align*}
    \der{E[e^{\gamma X}]}{\gamma} &= \sum_{i = 1}^{+\infty} \frac{\partial e^{\gamma x_i}}{\partial \gamma} Pr[x = x_i] = \sum_{i = 1}^{+\infty} x_i e^{\gamma x_i} Pr[x = x_i] \\
    &= \sum_{i \in P} x_i e^{\gamma x_i} Pr[x = x_i] + \sum_{i \in \mathbb{N}\setminus P} x_i e^{\gamma x_i} Pr[x = x_i] \\
    &\geq \sum_{i \in P} x_i (1 + {\gamma x_i}) Pr[x = x_i] + \sum_{i \in \mathbb{N}\setminus P} x_i Pr[x = x_i] \\
    &= E[X] + \gamma\sum_{i \in P} x_i^2 Pr[x = x_i]
\end{align*}

@@

$$\forall c > 0 \, \exists \gamma_c > 0 \, \forall \gamma \in (0, \gamma_c) : e^{\frac{\gamma^2 c}{2}} < E[e^{\gamma X}],$$

@@

In this section we will consider some specific family of continuos distributions with symmetric distribution density functions, because their expectation equals 0.

@@

\begin{align*}
    \infint{f(x)} &= \infint{c\expx{a}} = 1
\end{align*}

@@

\begin{align*}
    u &= x^a \\
    du &= dx\,(a x^{a - 1}) = dx\,(a u^{1 - \frac{1}{a}}),
\end{align*}

@@

Let's find n-th momentum of $X$ (expectation от $X^n$):

@@

\begin{align*}
    E[e^{\gamma X}] = E\left[\sum_{n = 0}^{+\infty}\frac{(\gamma X)^n}{n!}\right] &= \sum_{n = 0}^{+\infty}\gamma^n\frac{E[X^n]}{n!} = \sum_{n = 0}^{+\infty}\gamma^{2n}\frac{E[X^{2n}]}{2n!} =\\
    &= \sum_{n = 0}^{+\infty}\frac{(\gamma^2)^{n}}{n!}\left(\frac{E[X^{2n}]n!}{2n!}\right) = \sum_{n = 0}^{+\infty}\frac{(\gamma^2)^{n}}{n!} a_n
\end{align*}

@@

Consider sequence $\{\sqrt[n]{a_n}\}$:

\begin{align*}
    A = \lim_{n \to +\infty} \sqrt[n]{a_n} &= \lim_{n \to +\infty} \sqrt[n]{\frac{n! E[X^{2n}]}{2n!}} = 
    \lim_{n \to +\infty} \sqrt[n]{
        \frac{
            \left(\frac{n}{e}\right)^n \sqrt{2\pi n} \
            \Gamma\left(\frac{2n + 1}{a}\right)}{
                \left(\frac{2n}{e}\right)^{2n} \sqrt{4\pi n}\ \Gamma\left(\frac{1}{a}\right)}
        }\\
    &= \lim_{n \to +\infty} \frac{n}{e} \frac{e^2}{4n^2} \sqrt[n]{\Gamma\left(\frac{2n + 1}{a}\right)} \simeq \lim_{n \to +\infty}  \frac{e}{4n} \sqrt[n]{\left(\frac{2n + 1}{ae}\right)^{\frac{2n + 1}{a}}} \\
    &= \lim_{n \to +\infty} \frac{e}{4n} \left(\frac{2n}{ae}\right)^{\frac{2}{a}} = \left(\frac{e^{1 - \frac{2}{a}}}{2^{2 - \frac{2}{a}} a^\frac{2}{a}}\right) \lim_{n \to +\infty} n^{\frac{2}{a} - 1}.
\end{align*}

Let's take a look on convergence of previous sequence regarding to values of the $a$: 
\begin{caseof}
    \case{$a \geq 2$}{

        Then $A$ exist, which means existing $C > 0$ with property 
        $\forall n \geq 0 : a_n \leq C^n$.
        Hence $E[e^{\gamma X}] \leq e^{\gamma^2 C}.$
    }
    \case{$a < 2$}{

@@

$$\exists K > 0 \ \forall p \geq 1: \left(E[X^p]\right)^{\frac{1}{p}} \leq K \sqrt{p}.$$

@@

\begin{align*}
    E[X^p] &= \frac{\Gamma\left(\frac{p + 1}{a}\right)}{\Gamma\left(\frac{1}{a}\right)} \\
    E[X^p]^\frac{1}{p} &\underrel{p \to +\infty} {=} \left(\frac{p}{e a}\right)^{\frac{p}{a} \frac{1}{p}} = \mathcal{O}(p^\frac{1}{a}).
\end{align*}

@@

So both requirements are feasible since:

$$\exists \gamma_0 > 0 : \forall \gamma \in (0, \gamma_0) : E[e^{\gamma X}] < 1.$$

@@

@@

Since $\{Y_t\}_{t \in \mathbb{N}}$ is a process with negative drift, it is a subject to theorem \cite{}:

@@

Let $t_0 := \frac{\kappa (b - a)}{\varepsilon}$. 
\begin{align*}
    \Pr\left[T_X \leq \frac{\kappa (b - a)}{\varepsilon}\right] \leq \frac{\kappa (b - a)}{\varepsilon} D p e^{-\gamma(1 - \kappa)(b - a)}.
\end{align*}

@@

\begin{align*}
    \Pr\left[T_X > \frac{(b - a)}{2\varepsilon}\right] \leq \frac{(b - a)}{2\varepsilon} D p e^{-\gamma\frac{(b - a)}{2}}
\end{align*}

\subsection{Lower bounds}
% Lets take a look on process $\{X_t\}$ and its derivative process $\{Y_t\}$, where $Y_t = \varepsilon t - X_t$ and it has negative drift.

>>>>

\documentclass[12pt, a4paper]{article}
% \documentclass[8pt, a4paper, twocolumn]{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{indentfirst}
\usepackage{graphicx}
\usepackage{mathtext}
\usepackage[T1,T2A]{fontenc}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{stmaryrd}
\usepackage{a4wide}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{subcaption}

\lstset{basicstyle=\ttfamily\footnotesize,breaklines=true}
\definecolor{darkGreen}{RGB}{31, 140, 47}
\definecolor{darkBlue}{RGB}{31, 53, 125}   
\title{\text{Additive drift with tail bounds}}

@@

    If there are constants $\lambda > 0$, $D \ge 1$, and a $p > 1$ taking only positive values, for which the following four conditions hold
    \renewcommand\labelenumi{(\theenumi)}
    \begin{enumerate}
        \item $\gfun(X_0) \ge b$,
        \item $\forall t \ge 0 E\left[e^{-\lambda(\gfun(X_{t + 1} - \gfun(X_t)))} |\ X_t,\ \gfun(X_t) < b\right] \leq 1 - \frac{1}{p} =: \rho$,
        \item $\forall t \ge 0 E\left[e^{-\lambda(\gfun(X_{t + 1} - b))} |\ X_t,\ \gfun(X_t) \ge b\right] \leq D$,
    \end{enumerate}
    then for all time bounds $B \ge 0$ the probability that $T$ exceeds $B$ is at most

@@

\begin{lemma}[Lemma 2.8 in \cite{Hajek 82}] \label{lm:haj}
    If conditions 2 and 3 are met then for all $t \geq 0$ we have

@@

    \begin{align*}
        \Pr[T \leq B] & = \sum_{k=1}^{B} \Pr[T = k]                                                                        \\
                      & = \sum_{k=1}^{B} \Pr[\gfun(X_k) \leq a \land \gfun(X_{k - 1}) > a \land ... \land \gfun(X_0) > a)] \\
                      & \leq \sum_{k=1}^{B} \Pr[\gfun(X_k) \leq a].
    \end{align*}

@@

    \begin{align*}
        \Pr[T \leq B] & \leq \sum_{k=1}^{B} \left(\rho^k e^{\lambda(a - \gfun(X_0))} + \frac{1 - \rho^k}{1 - \rho} D e^{\lambda(a - b)}\right)                                                          \\
                      & = \rho \left(\frac{1 - \rho^B}{1 - \rho}\right) e^{\lambda a}\left(e^{-\lambda\gfun(X_0)} - \frac{D}{1 - \rho} e^{-\lambda b}\right) + e^{\lambda(a - b)} \frac{B D}{1 - \rho}.
    \end{align*}

@@

\end{proof}
\subsection{Theorem for sub-gaussian processes}
\cm
\subsection{Comparing requirements}
\label{sec:compare}
To use some versions of drift theorems, we need some requirements on the sequence of random variables to be satisfied, such as the following:
$$
    \exists \delta \geq 0,\ c \in \mathbb{R} \ \forall  t \geq 0 \ \forall \gamma \in [0, \delta] $$$$
    E\left[e^{\gamma (X_{t + 1} - X_{t})}\right] \leq e^{\frac{c \gamma^2}{2}},$$

@@

$$\exists \delta \geq 0,\ p \geq 1 \ \forall t \geq 0 $$$$
    E\left[e^{\gamma (X_{t + 1} - X_{t})}\right] \leq 1 - \frac{1}{p}\ .$$

@@

Consider the definition of expectation of a function
\[
    E[e^{\gamma X}] = \int_{-\infty}^{+\infty} f(x) e^{\gamma x} \,dx,
\]

where $f(x)$ is a probability density function.

@@

Let's take the first derivative $\gamma$

\begin{align*}
    \frac{\partial E[e^{\gamma X}]}{\partial \gamma} & = \frac{\partial}{\partial \gamma} \int_{-\infty}^{+\infty} f(x) e^{\gamma x} \, dx = \int_{-\infty}^{+\infty} f(x) \frac{\partial e^{\gamma x}}{\partial \gamma} \, dx = \int_{-\infty}^{+\infty} x f(x) e^{\gamma x} \, dx = \\
                                                     & = \int_{-\infty}^{0} x f(x) e^{\gamma x} \, dx + \int_{0}^{+\infty} x f(x) e^{\gamma x} \, dx.
\end{align*}

Note that $\forall x \leq 0 e^{\gamma x} \leq 1$ and $\forall x \geq 0 e^{\gamma x} \geq 1 + \gamma x$. Hence because $\forall x f(x) \geq 0$

\begin{align*}
    \int_{0}^{+\infty} x f(x) e^{\gamma x} \, dx & \geq \int_{0}^{+\infty} x f(x) (1 + \gamma x)\, dx \\
    \int_{-\infty}^{0} x f(x) e^{\gamma x} \, dx & \geq \int_{-\infty}^{0} x f(x)\, dx.
\end{align*}

@@

\begin{align*}
    \frac{\partial E[e^{\gamma X}]}{\partial \gamma} & \geq  \int_{0}^{+\infty} x f(x) (1 + \gamma x)\, dx + \int_{-\infty}^{0} x f(x)\, dx \\
                                                     & = E[X] + \gamma \int_{0}^{+\infty} x^2 f(x) \, dx.
\end{align*}

Denote $\int_{0}^{+\infty} x^2 f(x) \, dx = c \geq 0$ and then if we reintegrate back, we get a restriction on the expectation from below

@@

In the same way consider expectation of function by definition

@@

After taking the first derivative we may split terms from $P$ set with other terms
% В таком случае, аналогично возьмем производную и рассмотрим пот отдельности слагаемые из множества P и остальные:

\begin{align*}
    \der{E[e^{\gamma X}]}{\gamma} & = \sum_{i = 1}^{+\infty} \frac{\partial e^{\gamma x_i}}{\partial \gamma} Pr[x = x_i] = \sum_{i = 1}^{+\infty} x_i e^{\gamma x_i} Pr[x = x_i] \\
                                  & = \sum_{i \in P} x_i e^{\gamma x_i} Pr[x = x_i] + \sum_{i \in \mathbb{N}\setminus P} x_i e^{\gamma x_i} Pr[x = x_i]                          \\
                                  & \geq \sum_{i \in P} x_i (1 + {\gamma x_i}) Pr[x = x_i] + \sum_{i \in \mathbb{N}\setminus P} x_i Pr[x = x_i]                                  \\
                                  & = E[X] + \gamma\sum_{i \in P} x_i^2 Pr[x = x_i]
\end{align*}

@@

$$\forall c > 0 \, \exists \gamma_c > 0 \, \forall \gamma \in (0, \gamma_c) e^{\frac{\gamma^2 c}{2}} < E[e^{\gamma X}],$$

@@

In this section we will consider some specific family of continuos distributions with symmetric probability density functions, because their expectation equals 0.

@@

\begin{align*}
    \infint{f(x)} & = \infint{c\expx{a}} = 1
\end{align*}

@@

\begin{align*}
    u  & = x^a                                              \\
    du & = dx\,(a x^{a - 1}) = dx\,(a u^{1 - \frac{1}{a}}),
\end{align*}

@@

Let's find n-th momentum of $X$ (expectation от $X^n$)

@@

\begin{align*}
    E[e^{\gamma X}] = E\left[\sum_{n = 0}^{+\infty}\frac{(\gamma X)^n}{n!}\right] & = \sum_{n = 0}^{+\infty}\gamma^n\frac{E[X^n]}{n!} = \sum_{n = 0}^{+\infty}\gamma^{2n}\frac{E[X^{2n}]}{2n!} =                                \\
    & = \sum_{n = 0}^{+\infty}\frac{(\gamma^2)^{n}}{n!}\left(\frac{E[X^{2n}]n!}{2n!}\right) = \sum_{n = 0}^{+\infty}\frac{(\gamma^2)^{n}}{n!} a_n
\end{align*}

@@

Consider sequence $\{\sqrt[n]{a_n}\}$

\begin{align*}
    A = \lim_{n \to +\infty} \sqrt[n]{a_n} & = \lim_{n \to +\infty} \sqrt[n]{\frac{n! E[X^{2n}]}{2n!}} =
    \lim_{n \to +\infty} \sqrt[n]{
        \frac{
            \left(\frac{n}{e}\right)^n \sqrt{2\pi n} \
            \Gamma\left(\frac{2n + 1}{a}\right)}{
            \left(\frac{2n}{e}\right)^{2n} \sqrt{4\pi n}\ \Gamma\left(\frac{1}{a}\right)}
    } \\
    & = \lim_{n \to +\infty} \frac{n}{e} \frac{e^2}{4n^2} \sqrt[n]{\Gamma\left(\frac{2n + 1}{a}\right)} \simeq \lim_{n \to +\infty}  \frac{e}{4n} \sqrt[n]{\left(\frac{2n + 1}{ae}\right)^{\frac{2n + 1}{a}}} \\
    & = \lim_{n \to +\infty} \frac{e}{4n} \left(\frac{2n}{ae}\right)^{\frac{2}{a}} = \left(\frac{e^{1 - \frac{2}{a}}}{2^{2 - \frac{2}{a}} a^\frac{2}{a}}\right) \lim_{n \to +\infty} n^{\frac{2}{a} - 1}.
\end{align*}

Let's take a look on convergence of previous sequence regarding to values of the $a$
\begin{caseof}
    \case{$a \geq 2$}{

        Then $A$ exist, which means existing $C > 0$ with property
        $\forall n \geq 0 a_n \leq C^n$.
        Hence $E[e^{\gamma X}] \leq e^{\gamma^2 C}.$
    }
    \case{$a < 2$}{

@@

$$\exists K > 0 \ \forall p \geq 1 \left(E[X^p]\right)^{\frac{1}{p}} \leq K \sqrt{p}.$$

@@

\begin{align*}
    E[X^p]             & = \frac{\Gamma\left(\frac{p + 1}{a}\right)}{\Gamma\left(\frac{1}{a}\right)}                                     \\
    E[X^p]^\frac{1}{p} & \underrel{p \to +\infty} {=} \left(\frac{p}{e a}\right)^{\frac{p}{a} \frac{1}{p}} = \mathcal{O}(p^\frac{1}{a}).
\end{align*}

@@

So both requirements are feasible since

$$\exists \gamma_0 > 0 \forall \gamma \in (0, \gamma_0) E[e^{\gamma X}] < 1.$$

@@

Define function for distribution $X$ $B_X$ such that
\begin{align*}
    B_X(\gamma) = 1 + \gamma E[X] + \frac{\gamma^2}{2} E[X^2]_+,
\end{align*}

Where
\[
E[X^2]_+= 
\begin{cases}
    \int_0^{+\infty} x^2 f(x)\, dx,& \text{if $X$ is continuos}\\
    \sum_{x \geq 0} x^2 \Pr[X = x],              & \text{otherwise}.
\end{cases}
\]

Also define function $Ee_X(\gamma) = E[e^{\gamma X}]$. We proofed in end of section \ref*{sec:compare} that

\begin{align*}
    \forall \gamma\geq 0: Ee_X(\gamma) \geq B_X(\gamma).
\end{align*}

If $Ee(\gamma)$ is a differentiable function, then by definition the derivative will be continuos. Since $e^{\gamma x}$ and $f(x)$ is non-negative for all $x$ and $\gamma$, hence

\begin{align*}
    \frac{\partial^2 Ee(\gamma)}{\partial\gamma^2} = \infint{x^2 f(x) e^{\gamma x}} > 0.
\end{align*}

Then
\begin{align*}
    \der{Ee(\gamma)}{\gamma} \Big|_{\gamma = \gamma_0} - \der{Ee(\gamma)}{\gamma}\Big|_{\gamma = 0} &= \int_0^{\gamma_0} \frac{\partial^2 Ee(\gamma)}{\partial\gamma^2}\, d\gamma > 0 \\
    \der{Ee\left(\gamma_0\right)}{\gamma} &= E[X] + \int_0^{\gamma_0} \frac{\partial^2 Ee(\gamma)}{\partial\gamma^2}\, d\gamma
\end{align*}

Since second derivative always great than zero, than first derivative is continuously growing.

Then if $E[X] < 0$ $Ee(\gamma)$ would go down in some neighborhood. And if $E[X^2]_+ \neq 0$ it will have point with zero derivative, what fits the condition of the second requirement.

\pagebreak

Example for distribution $X$ with probability density function $f(x) = 0.65 e^{-0.65(x + 2)}$:

\begin{figure}[h!]
    \begin{center}
     \begin{tikzpicture}[scale = 0.8]
        \begin{axis}[
            axis lines = left,
            xlabel = \(\gamma\),
            ylabel = {\(f(\gamma)\)},
            xmin=0, xmax=1,
            ymin=0.9, ymax=1.2
        ]
        \addplot[color=darkGreen,
            domain=0:0.9,
            dashed,
            line width=1pt
        ]{1 + (-0.4615) * x + (1.2901) / 2 * x * x};
        \addlegendentry{\(B_X(\gamma)\)}

        \addplot[color=darkBlue,
            domain=0:0.6,
            line width=1.2pt
        ]{-0.65/(x - 0.65) * exp(-2 * x)};
        \addlegendentry{\(Ee_X(\gamma)]\)}

        \addplot[color=black,mark=*] coordinates {(0.3578, 0.9174)};
        \addplot[color=black,mark=*] coordinates {(0.15, 0.9631)};
        \addplot[color=red,
            domain=0:3,
            dashed
        ]{1};
        \end{axis}
     \end{tikzpicture}
    \end{center}
    % \caption{Plot of the function $Ee_X(\gamma)$ with its bound $B_X(\gamma)$, where $X$ has probability density function $f(x) = 0.65 e^{-0.65(x + 2)}$.}
    % \label{fig:negativeDriftPic2}
\end{figure}

If $E[X] > 0$ then in some neighborhood around $\gamma = 0$ would be greater than any $e^{\frac{c \gamma^2}{2}}$, because if

$g(0) = 0 < E[X]$ and $Ee_X(0) = B_X(0) = 1$. Hence both of requirements are not feasible.

Example

\begin{figure}[h!]
    \begin{center}
     \begin{tikzpicture}[scale = 0.8]
        \begin{axis}[
            axis lines = left,
            xlabel = \(\gamma\),
            ylabel = {\(f(\gamma)\)},
            xmin=0, xmax=0.4,
            ymin=0.95, ymax=1.5
        ]
        % \addplot[color=darkGreen,
        %     domain=0:0.9,
        %     dashed,
        %     line width=1pt
        % ]{1 + (1) * x + (1.925) / 2 * x * x};
        % \addlegendentry{\(B_X(\gamma)\)}
        \addplot[color=green,
            domain=0.04:0.3,
            line width=0.8pt
        ]{exp((50 * x^2) / 2)};

        \addplot[color=red,
            domain=0:0.6,
            line width=0.8pt,
            dashed
        ]{exp((4 * x^2) / 2)};

        \addplot[color=red,
            domain=0:0.6,
            line width=0.8pt,
            dashed
        ]{exp((10 * x^2) / 2)};

        \addplot[color=green,
            domain=0.1:0.6,
            line width=0.8pt
        ]{exp((20 * x^2) / 2)};

        % \addplot[color=red,
        %     domain=0:0.6,
        %     line width=1.2pt
        % ]{exp((15 * x^2) / 2)};

        \addplot[color=red,
            domain=0:0.6,
            line width=0.8pt,
            dashed
        ]{exp((20 * x^2) / 2)};

        \addplot[color=red,
            domain=0:0.3,
            line width=0.8pt,
            dashed
        ]{exp((50 * x^2) / 2)};

        \addplot[color=darkBlue,
            domain=0:0.6,
            line width=1.2pt
        ]{exp((x^2 + 2*x) / 2)};

        \addlegendentry{\(Ee_X(\gamma)\)}

        % \addplot[color=black,mark=*] coordinates {(0.3578, 0.9174)};
        % \addplot[color=black,mark=*] coordinates {(0.15, 0.9631)};
        \addplot[color=red,
            domain=0:3,
            dashed
        ]{1};
        \end{axis}
     \end{tikzpicture}
    \end{center}
    % \caption{Plot of the function $Ee_X(\gamma)$ with its bound $B_X(\gamma)$, where $X$ has probability density function $f(x) = 0.65 e^{-0.65(x + 2)}$.}
    % \label{fig:negativeDriftPic2}
\end{figure}

@@

Since $\{Y_t\}_{t \in \mathbb{N}}$ is a process with negative drift, it is a subject to Theorem \cite{}. Hence, we have

@@

Let $t_0 := \frac{\kappa (b - a)}{\varepsilon}$. Then we compute
\begin{align*}
    \Pr\left[T_X \leq \frac{\kappa (b - a)}{\varepsilon}\right] \leq \frac{\kappa (b - a)}{\varepsilon} D p e^{-\gamma(1 - \kappa)(b - a)}.
\end{align*}

@@

\begin{align*}
    \Pr\left[T_X \leq \frac{(b - a)}{2\varepsilon}\right] \leq \frac{(b - a)}{2\varepsilon} D p e^{-\gamma\frac{(b - a)}{2}}.
\end{align*}

\subsection{Lower bounds}

Consider a process $\{X_t\}_{t \in \mathbb{N}}$ with positive drift (i.e. $E[X_{t + 1} - X_t |\ X_t = s] \geq 0$ for all $s$) and another process $\{Y_t\}_{t \in \mathbb{N}}$ such that $Y_t = \varepsilon t - X_t$ and it has negative drift (i.e. $E[Y_{t + 1} - Y_t |\ Y_t = s] \leq 0$ for all $s$).

Our aim is to bound the probability $\Pr[T_X > t_0]$, where $T_X$ is the first time when $X_t \geq b$ for some $b > X_0$ and for $t_0$. We first note that

\begin{align*}
    \Pr[T_X > t_0] \leq \Pr[X_{t_0} < b] \leq \Pr[Y_{t_0} > \varepsilon t_0 - b].
\end{align*}

Since $\{Y_t\}_{t \in \mathbb{N}}$ is a process with negative drift, it is a subject to Theorem \cite{}. Hence, we have

\begin{align*}
    \Pr[Y_t > \varepsilon t_0 - b] \leq t_0 D p e^{-\gamma(\epsilon t_0 - b + a)},
\end{align*}

\begin{align*}
    \Pr[T_X > t_0] \leq t_0 D p e^{-\gamma(\epsilon t_0 - b + a)}.
\end{align*}

Let $t_0 := \frac{\kappa (b - a)}{\varepsilon}$. Then we compute
\begin{align*}
    \Pr\left[T_X > \frac{\kappa (b - a)}{\varepsilon}\right] \leq \frac{\kappa (b - a)}{\varepsilon} D p e^{-\gamma(\kappa - 1)(b - a)}.
\end{align*}

For example we can use $\kappa = \frac{3}{2}$ and obtain

\begin{align*}
    \Pr\left[T_X > \frac{3 (b - a)}{2\varepsilon}\right] \leq \frac{3(b - a)}{2\varepsilon} D p e^{-\gamma\frac{(b - a)}{2}}.
\end{align*}

% Lets take a look on process $\{X_t\}$ and its derivative process $\{Y_t\}$, where $Y_t = \varepsilon t - X_t$ and it has negative drift.
